---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# CPTraceR

<!-- badges: start -->
<!-- badges: end -->

The goal of CPTraceR is to add unique track ids to CellProfiler tracking output.

## Installation

You can install the development version of CPTraceR with:

``` r
remotes::install_github("burgerga/CPTraceR")
```

## Example

Assuming `data` contains some data from a CellProfiler tsv:

```{r, echo=F, message = FALSE}
library(tidyverse)
data <-  read_tsv(file.path("~/Downloads","20190925_BrittData_singleCell_1hrDelay_withoutT01.txt"))
```

The original data:

```{r}
library(tidyverse)
data_select <- data %>%
  select(groupNumber, 
         groupInd, 
         par_obj_num = Nuclei_TrackObjects_ParentObjectNumber_30, 
         obj_num     = Nuclei_Number_Object_Number)
# example output from the first group
data_select %>% 
  filter(groupNumber == 1) %>%
  arrange(obj_num, groupInd)
```

Let's fix the output:

```{r}
library(CPTraceR)
library(progressr) #enable progress bars
with_progress({
  fixed <- createLUTGroup(data_select %>% filter(groupNumber == 1) %>% select(-groupNumber)) 
})
fixed %>% 
  arrange(obj_num, groupInd)
```

Three new columns are added:

* `cid`: id of the original cell (daughter cells share `cid` with parent)
* `uid`: unique id (daughter cells don't share `uid` with parent)
* `alt_obj_num`: character id of cells that show lineage with suffixes

```{r}
fixed %>% 
  filter(groupInd == 2) %>%
  arrange(obj_num, groupInd)
```

Now run everything sequentially:

```{r}
library(tictoc)
tic()
with_progress({
  createLUT(data_select) 
})
toc()
```

Now run everything in parallel:

```{r}
library(tictoc)
library(future)
plan(multisession)
tic()
with_progress({
  createLUT(data_select) 
})
toc()
```
